---
title: "Homework5"
output: html_document
date: "2023-05-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 3.1 Import

Set up libraries and import

```{r}
#Load ggplot2 to visualize data
library('ggplot2')
#load readr to import CSV
library(readr)

Iris <- read.csv('./Iris.csv')
class(Iris)

head(Iris)
```

# 3.2 Scatter Plot

make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors.

```{r}
ggplot(data=Iris,aes( x=SepalLengthCm, y=SepalWidthCm, color=Species)) + geom_point() + theme_minimal() + ggtitle("Sepal Length vs. Sepal width") + xlab("Sepal Length in cm") + ylab("Sepal Width in cm")

```

# 3.3 Regression Line

add regression line for the previous plot with the whole data set (regardless of the species)

```{r}
a = ggplot(data=Iris,aes( x=SepalLengthCm, y=SepalWidthCm)) + geom_point() + theme_minimal()

b = a +geom_smooth(method = "lm",
              formula = y ~ x)

b
```

# 3.4 Pearson correlation

calculate the Pearson correlation for this plot

```{r}


correlation <- cor(Iris$SepalLengthCm, Iris$SepalWidthCm )
correlation

```

# 3.5 Box plot

make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors

```{r}
ggplot(data=Iris,aes(x=Species, y=PetalWidthCm,color=Species)) + geom_boxplot() +theme_minimal()

```

# 3.6. Histogram

make the histogram for Petal.Width with 3 species separately in x-axis in different colors

```{r}
ggplot(data=Iris,aes(x=PetalWidthCm, fill=Species)) + geom_histogram() 

```

# T-Test

run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species

##Conclusion
The width is...

```{r}
#Filter Dataset so it only includes the two desired species
pwSet <- Iris$PetalWidthCm[(Iris$Species == "Iris-setosa")]
pwVirg <- Iris$PetalWidthCm[(Iris$Species == "Iris-virginica")]
#T-Test
t.test(pwSet,pwVirg)

```
